---
title: "reading_data_from_the_web"
author: "AnMei Chen"
date: "10/19/2021"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis" , 
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## scape a table 

Extract only the first table from [this website](http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm)

```{r}
#read in the html
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

# use read_html from rvest
drug_use_html = read_html(url) 

```

Extract all 15 tables from the html, based on knowing that a table in html is often indicated as "table". Then focus of the first one.Then remove the first row.

```{r}
tabl_marj = 
  drug_use_html %>% 
  html_nodes(css = "table") %>% 
  first() %>% 
  html_table() %>% 
  slice(-1) 
```


```{r}
drug_use_df =
  drug_use_html %>% 
  html_table() %>% 
  first() %>% 
  slice(-1)
```


## Star Wars Movie Info

I want the data from [here](https://www.imdb.com/list/ls070150896/)

```{r}
sw_url = "https://www.imdb.com/list/ls070150896/"

sw_html = read_html(sw_url)
  
```

Grab elements that I want.

```{r}
sw_titles =
  sw_html %>% 
  html_elements(".lister-item-header a") %>% 
  html_text()

sw_revenue =
  sw_html %>%
  html_elements(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

sw_r =
  sw_html %>%
  html_elements(".text-muted .ghost~ .text-muted+ span") %>%
  html_text()

sw_runtime = 
  sw_html %>%
  html_nodes(".runtime") %>%
  html_text()

sw_df = 
  tibble(
    title = sw_titles,
    revenue = sw_revenue,
    runtime = sw_runtime
  )

```

Dynamite reveiws

I want the data from [link](https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1)
```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(dynamite_url)

dynamite_review_tables = 
  dynamite_html %>% 
  html_elements(".a-text-bold span") %>% 
  html_text()

dynamite_stars =
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>% 
  html_text()

dynamite_df = 
  tibble(
    titles = dynamite_review_tables,
    starts = dynamite_stars
  )
```

## APIs

Get some data from an API about water

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% 
  content("parsed")

# use content() to parse this csv into a dataset
```

Json

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()
```

##BRFSS

BRFSS data via APIs
same process, different data

```{r}
brfss_df = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000)) %>% 
  content("parsed")
```

##some data aren't so nice...

Lets look at pokemon API ...

```{r}
poke_data = 
  GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()

poke_data[["name"]]
poke_data[["height"]]
poke_data[["abilities"]]

poke_data$name
poke_data$height
poke_data$abilities

```

If you need to access the data multiple times, it is better for you to have a rmd file to access and process the data from the internet and then use another rmd file to access your processed data from the other rmd file.